---
title: "Bernoulli Distribution"
author: "Brandon Parmanand"
date: '2022-07-28'
output: html_document
---


### Assignment

#### Find an event that has two possible outcomes, and that you can observe repeatedly. Such as flipping heads on a coin, rolling snake-eyes on two dice, etc.

##### Observe the event at least 30 times. Record a success as a 1 and failure as 0.
##### Compute the sample mean and the sample variance.
##### Plot a histogram of your results.
##### Use your observations to estimate $p$.
##### Run the density, cumulative distribution function, quantile function and random number generation code with prob equal to your estimated $p$.
##### Put your results in a document, upload your document to Canvas.

```{r}
setwd("C:/Users/brand/OneDrive/Documents/GitHub/Prob&Stats")
getwd()

library(readxl)
x <- read_excel("coinflip.xlsx", col_names = FALSE)
```


```{r}
coinflip <- as.numeric(x$...1)

mean(coinflip)
var(coinflip)

hist(coinflip)

table(coinflip)
# p = P(X=1)
p <- 16/30

dbinom(
  x = 0:1,
  size = 1,
  prob = p
)

pbinom(
  q = c(
    0,0.24,0.5,0.75,1
  ),
  size = 1,
  prob = p
)  

qbinom(
  p = c(
    0,0.24,0.5,0.75,1
  ),
  size = 1,
  prob = p
)
  
  
rbinom(
  n = 30,
  size = 1,
  prob = p
)
  
```

