---
title: "Discrete uniform distribution"
author: "Brandon Parmanand"
date: '2022-07-29'
output: html_document
---


### Assignment

#### Get some dice. You may use the more exotic dice from a game store.

#### Roll one die at least 30 times.

#### Create a table with these columns:

#### value 1-6, count, observed probabilities, discrete uniform probabilities, difference between the probabilities

#### Plot a histogram of your observations

```{r}

setwd("C:/Users/brand/OneDrive/Documents/GitHub/Prob&Stats")
getwd()

library(readxl)


```


### One die was rolled 30 times. Number of outcomes for each possible outcomes were tabulated and probability of the outcome was calculated. Discrete unifrom probability was 16.7% and the difference was taken
```{r}
x <- read_excel("dieroll.xlsx", col_names = TRUE)
x
```

### Here are the histograms of the data
```{r}
hist(x$Outcome, main = "Histogram of Outcomes")
hist(x$Prob, main = "Histogram of Observed Probabilities")
hist(x$Prob_Diff, main = "Histogram of Probabilities Differences")  
```

