---
title: "Exponential Distribution"
author: "Brandon Parmanand"
date: "july, 29 2022"
output: html_document
---
### For this assignment you are going to use your Poisson data results to analyze the corresponding exponential distribution.
### Set rate = x_bar where x_bar is your sample average from your Poisson assignment.
### Use dexp() to get the density for the numbers in [0, 10/rate]. Plot the density.
### Use pexp() to get the cumulative distribution for the integers in [0, 10/rate]. Plot the cdf.
### Use qexp() to get the quantile of your density. 0,0.25,0.5,0.75,1


### Density 

```{r}
rate <- 4.15
v <- seq(
  from = 0,
  to = 10/rate,
  by = 0.01
)
dexp_v <- dexp(
  x = v,
  rate = rate
)
plot(
  x = v,
  y = dexp_v,
  type = "l",
  main = "Probability density function of exponential distribution\n mean = 4.15"
)

```

### Cumulative Distribution

```{r}
pexp_v <- pexp(
  q = seq(
    from = 0,
    to = 10/rate,
    by = 0.01
  ),
  rate = rate
)
plot(
  x = v,
  y = pexp_v,
  type = "l",
  main = "Cumulative distribution function of exponential distribution\n mean = 4.15"
)
```

### Quantile of Density

```{r}
qexp(
  p = c(
    0,0.25,0.5,0.75,1
  ),
  rate = rate
)
```


