---
title: "Gamma Distribution"
author: "Brandon Parmanand"
date: "july, 29 2022"
output: html_document
---
### For this assignment you are going to simulate data from a gamma random variable, then analyze the data (pretending you do not know that the data is gamma.)

### Use runif() and qexp() to randomly generate 100 exponential random variables with parameter = 10. Do not use rexp().

### se runif() and qgamma() to randomly generate 100 gamma random variables with parameters = 10 and 10. Do not use rgamma().

### Use runif() and qnorm() to randomly generate 100 standard normal random variables. Do not use rnorm().

### Use runif() and qlnorm() to randomly generate 100 standard log-normal random variables. Do not use rlnorm().


```{r}

x <- runif(
  n = 100,
  min = 0,
  max = 1
)



qexp(
  p = c(
    0,0.25,0.5,0.75,1
  ),
  rate = 1
)


v_rgamma <- rgamma(
  n = 100,
  shape = 5,
  rate = 2
)
hist(
  x = v_rgamma,
  main = "histogram of randomly generated gamma random variables"
)


```

### Compute mean() and var() of your data. Use the gamma population mean and population variance to estimate the parameters of the gamma distribution.

```{r}
gamma_mean <- mean(v_rgamma)
gamma_var <- var(v_rgamma)

alpha <- (gamma_mean^2)/gamma_var
beta <- (gamma_mean/gamma_var)
```

### Use dgamma() to get the density for the values in [0, 5*x_bar]. Plot the density.

```{r}
x <- seq(
  from = 0,
  to = 5*gamma_mean,
  by = 0.001
)
dgamma_x <- dgamma(
  x = x,
  shape = alpha,
  rate = beta
)
plot(
  x = x,
  y = dgamma_x,
  main = "probability density function of a gamma random variable",
  type = "l"
)

```

### Use pgamma() to get the cumulative distribution for the values in [0, 5*x_bar]. Plot the cdf.

```{r}
pgamma_x <- pgamma(
  q = x,
  shape = alpha,
  rate = beta
)
plot(
  x = x,
  y = pgamma_x,
  main = "cumulative distribution function of a gamma random variable",
  type = "l"
)

```

### Use qgamma() to get the quantile of your density. 0,0.25,0.5,0.75,1

```{r}
qgamma(
  p = c(
    0,0.25,0.5,0.75,1
  ),
  shape = alpha,
  rate = beta
)

```

