---
title: "Geometric distribution"
author: "Brandon Parmanand"
date: '2022-07-28'
output: html_document
---


### Assignment

#### Select a Bernoulli event that you can easily do repeatedly. Determine which event is a success, which event is a failure.
#### Run your event until your first success. Recorde the number of trials (or failures). Repeat this until you have thirty or more observations.
#### Make a table of your data.
#### Plot a bar plot of your data.
#### Use your sample mean and the expected value to estimate p.
#### Use your estimated value of p to create a bar plot showing the density of a geometric random variable. How does your data bar plot compare to your density bar plot?
#### Run the example R code above with your estimated p as the probability.

```{r}
setwd("C:/Users/brand/OneDrive/Documents/GitHub/Prob&Stats")
getwd()

library(readxl)
x <- read_excel("coinfailures.xlsx", col_names = TRUE)
```

The Bar Plots are identical but instead of decreasing bar heights, they are increasing

```{r}

coinflip <- as.numeric(x$Failures)

failure_tbl <- table(coinflip)

barplot(failure_tbl, main="BarPlot of Counts of Failures Before Flipping Heads",
        xlab = "# of Failures before Flipping Heads")

mean <- mean(coinflip)

# E(X) = (1-p)/p
# E(X)= sample mean = 0.9333 
# 0.9333 = (1-p)/p
p = 0.5173 


density_tbl <- table(dgeom(
  x = coinflip,
  prob = p
))

barplot(density_tbl, main="Density Barlplot",
        xlab = "Density of  Failures before Flipping Heads")

```

### 

```{r}
dgeom(
  x = 0:10,
  prob = p
  )


pgeom(
  q =0:10,
  prob = p
)


qgeom(
  p = c(
    0,0.25,0.5,0.75,1
  ),
  prob = p
)


rgeom(
  n = 100,
  prob = p
)


# p <- 13/30
# q <- 1-p
# 
# EV <- q/p
  
```

