---
title: " linear regression hypothesis tests"
author: "Brandon Parmanand"
date: "July 31, 2022"
output: html_document
---
### Take your multiple linear regression model from your previous assignment.

### Run the hypothesis tests from the video that use summary() and anova().

### For each hypothesis test:

### State your hypotheses, Ho and Ha.
### State your conclusion in terms of failing to reject the null hypothesis, and reject the null hypothesis in favor of the alternative. (small p-value leads to rejecting the null)
### State your conclusion in plain language (how you would state your conclusion to a non-statistician)

```{r}
options(
  digits = 2
)
```

# Load the data


```{r}
setwd("C:/Users/brand/OneDrive/Documents/GitHub/Prob&Stats")
getwd()

movies <- read.csv("movies.csv")
movies <- na.omit(movies)
# rownames(movies) <- movies$title
head(movies)
movies$binary_best_pic_nom <- ifelse(movies$best_pic_nom=="yes",1,0)
lm_4 <- lm(
  formula = audience_score~imdb_rating+runtime+critics_score+imdb_num_votes+binary_best_pic_nom,
  data = movies
)

lm_3 <- update(
  object = lm_4,
  formula = ~. - binary_best_pic_nom
)

```




```{r}
summary(
  object = lm_4
)
anova(
  object = lm_4
)
```


# Is there something in the model bringing value?

For this test, we want to see if one or more of the predictor variables are useful in modeling the target variable.

$$\begin{align}
Ho:& \beta_1 = \beta_2 = \beta_3 = ... = \beta_p = 0 \\
Ha:& \text{One or more slopes do not equal zero.}
\end{align}$$


Reject the null hypothesis in favor of the alternative. I conclude that one or more slopes are not equal to 0. The p-value is very small
We are saying that one or more of the predictor variables are bringing value to the model.


# Which predictors are bringing value to the model?

We can evaluate each coefficient using hypothesis testing. If a coefficient is non-zero, then we conclude that the predictor variable is bringing informative value in modeling the target variable.

$$\begin{align}
Ho:& \beta_j = 0 \\
Ha:& \beta_j \ne 0
\end{align}$$

Use the coefficient $Pr(>|t|)$ to evaluate each hypothesis test.

imdb_rating - p value small, Reject null hypothesis in favor of the alternative. I conclude it is not = 0        
runtime - p value small, Reject null hypothesis in favor of the alternative. I conclude it is not = 0            
critics_score - p value small, Reject null hypothesis in favor of the alternative. I conclude it is not = 0       
imdb_num_votes  - Fail to reject the null hpyothesis. I conclude this predictor coefficient is = 0       
binary_best_pic_nom - Fail to reject the null hpyothesis. I conclude this predictor coefficient is = 0 

Using this hypothesis tests, i can see which predictors are bringing value to the model. We may be able to remove some predictors that are not bringing sufficient value

# Should I use a simplier model?

Here we compare models to see if they are equally informative.

$$\begin{align}
Ho:& \text{The models are equally informative (use simplier model)} \\
Ha:& \text{The models are not equally informative (use more complicated model)}
\end{align}$$

We have two way of comparing models.

* Compare models were predictors are sequentially added to a simplier model
* Compare two models of interest

## Sequential models

```{r}

anova(
  object = lm_4
)
```
For imbd_rating critics_score, and runtime the p value is small.Reject null hypothesis in favor of the alternative. imbd_num_votes and binary_best_pic_nom are both greater than the test statistic. Fail to reject the null hypthesis
These two predictor variables do not bring as much value as the frst three variables. Can create new model with reduced predictors
## Compare two specific models 

```{r}
anova(
  lm_3,lm_4
)
```
Fail to reject the null hypothesis. The reduced model LM3 brings the same value the full model LM4



```{r}
car::linearHypothesis(
  model = lm_4,
  hypothesis.matrix = diag(6),
  rhs = c(-31,10,0,0,0,4)
)
```

Reject the null hypothesis. This hypothesis test concludes these models are different than the LM4

```{r}
car::linearHypothesis(
  model = lm_4,
  hypothesis.matrix = diag(6),
  rhs = c(-31,10,0,0,0,4),
  test = "Chisq"
)
```

Reject the null hypothesis. This hypothesis test concludes these models are different than the LM4





