---
title: "Multiple linear regression"
author: "Brandon Parmanand"
date: "July 31, 2022"
output: html_document
---

Let's create a linear model with one target variable and multiple predictor variables.

```{r}
options(
  digits = 2
)
```

# Load the data


```{r}
setwd("C:/Users/brand/OneDrive/Documents/GitHub/Prob&Stats")
getwd()

movies <- read.csv("movies.csv")
movies <- na.omit(movies)
# rownames(movies) <- movies$title
head(movies)
```

# Define plot colors

```{r}
v <- seq(
  from = min(movies$audience_score),
  to = max(movies$audience_score),
  by = 1
)
v_color <- viridis::viridis(
  n = length(v)
)
names(v_color) <- v
movies$color <- v_color[as.character(movies$audience_score)]
```

# Explore the multivariate data

```{r}
movies$binary_best_pic_nom <- ifelse(movies$best_pic_nom=="yes",1,0)
pairs(
  formula = audience_score~imdb_rating+runtime+critics_score+imdb_num_votes+binary_best_pic_nom,
  data = movies,
  col = movies$color,
  pch = 19
)
boxplot(
  formula = audience_score ~ binary_best_pic_nom,
  data = movies,
  col = "steelblue"
)
rug(
  x = jitter(movies$audience_score[movies$binary_best_pic_nom == 0]),
  side = 2
)
rug(
  x = jitter(movies$audience_score[movies$binary_best_pic_nom == 1]),
  side = 4
)
```

```{r}
lm_4 <- lm(
  formula = audience_score~imdb_rating+runtime+critics_score+imdb_num_votes+binary_best_pic_nom,
  data = movies
)
summary(
  object = lm_4
)
anova(
  object = lm_4
)
plot(
  x = lm_4,
  which = 1:6,
  bg = movies$color,
  pch = 21
)

lm_3 <- update(
  object = lm_4,
  formula = ~. - binary_best_pic_nom
)
summary(
  object = lm_3
)
anova(
  object = lm_3
)
anova(lm_3,lm_4)
plot(
  x = lm_3,
  which = 1:6,
  bg = movies$color,
  pch = 21
)
```

# Wait, how many hypothesis tests are there?

The summary() function evaluates the hypothesis that a coefficient equals zero.

The anova() function compares models to each other. There are always at least two models in an anova() test.

Notice that the only difference between these linear models is the order of the predictor variables in the formulas.

```{r}
lm_dfes <- lm(
  formula = audience_score~imdb_rating+runtime+critics_score+imdb_num_votes+binary_best_pic_nom,
  data = movies
)
lm_sefd <- lm(
  formula = audience_score~binary_best_pic_nom+imdb_num_votes+critics_score+runtime+imdb_rating,
  data = movies
)
```

## summary()

The summary() function evaluates if a coefficient equals zero. Order within the formula does not matter.

```{r}
summary(
  object = lm_dfes
)
summary(
  object = lm_sefd
)
```

## anova()

The anova() function two models, one of the model's predictor variables are a subset of the other's predictor variables. The hypothesis test is evaluating if adding a predictor variable is worth the additional complexity in the model.

```{r}
anova(
  object = lm_dfes
)
anova(
  object = lm_sefd
)
```