---
title: "Negative-Binomial distribution"
author: "Brandon Parmanand"
date: '2022-07-28'
output: html_document
---


### Assignment

#### Select a negative binomial event that you can easily do repeatedly. Set the number of successes to 3. Determine which event is a success, which event is a failure.
#### Run your event until your 3rd success. Record the number of trials (or failures). Repeat this until you have thirty or more observations.
#### Make a table of your data.
#### Plot a histogram of your data.
#### Use your sample and the population expected value to estimate p.
#### Use your estimated value of p to create a bar plot showing the density of the random variable. How does your data bar plot compare to your density bar plot?
#### Run the example R code above with your estimated p as the probability.

```{r}

setwd("C:/Users/brand/OneDrive/Documents/GitHub/Prob&Stats")
getwd()

library(readxl)
x <- read_excel("threesuccess.xlsx", col_names = TRUE)

```

The Bar Plots are identical but instead of decreasing bar heights, they are increasing

```{r}

coinflip <- as.numeric(x$Failures)

failure_tbl <- table(coinflip)

barplot(failure_tbl, main="Counts of Failures Before 3 Successs of Flipping Heads",
        xlab = "# of Failures before Flipping 3 Heads")

mean <- mean(coinflip)

# E(X) = r(1-p)/p
# E(X)= sample mean = 0.9333 
# r= # of sucesses = 3
# 2.7 = 3(1-p)/p
p = 0.5263


density_tbl <- table(dnbinom(
x = coinflip,
size = 3,
prob = p
))

barplot(density_tbl, main="Density Barlplot",
        xlab = "Density of Failures before Flipping 3 Heads")




```

### 

```{r}
dnbinom(
  x = 0:20,
  size = 5,
  prob = p
)

pnbinom(
  q = 0:20,
  size = 5,
  prob = p
)

qnbinom(
  p =c(
    0,0.25,0.5,0.75,1
  ),
  size = 5,
  prob = p
)

rnbinom(
  n = 100,
  size = 5,
  prob = p
)
  
```

