---
title: "A first linear model"
author: "Brandon Parmanand"
date: "July 31, 2022"
output: html_document
---


# Set up the work space

First I want to reduce the number of displayed digits.

```{r}
options(
  digits = 2
)
```

# Load the data


```{r}
setwd("C:/Users/brand/OneDrive/Documents/GitHub/Prob&Stats")
getwd()

movies <- read.csv("movies.csv")
```

Let's look at our data.

```{r}
head(movies)
summary(
  object = movies
)
```

This is a regression class, so let's plot a scatter plot. We do this to see if building a regression model is reasonable.

```{r}
par(
  mfrow=c(1,1)
)
plot(
  x = movies$critics_score,
  y = movies$audience_score,
  xlab="Rotten Tomatoes Critics Score", 
  ylab="Rotten Tomatoes Audience Score"
)
```

# A simple linear regression model

Let's build a simple linear regression model.

```{r}
lm_movies <- lm(
  formula = audience_score~critics_score,
  data = movies
)
```

Now let's put the linear model on our scatter plot to see if the model is reasonable.

```{r}
plot(
  x = movies$critics_score,
  y = movies$audience_score,
  xlab="Rotten Tomatoes Critics Score", 
  ylab="Rotten Tomatoes Audience Score"
)
abline(
  reg = lm_movies,
  col = "red"
)
```

# Hypothesis testing

Hypothesis testing is critical to small data analytics. anova() and summary() give us the most important tests for linear regression.

```{r}
anova(
  object = lm_movies
)
summary(
  object = lm_movies
)
```

Let's check those t-values from the summary() output.

```{r}
33.43551/1.27561
0.50144/0.01984

```

# Confidence intervals for the coefficients

Now let's look at confidence intervals for the coefficients.

```{r}
confint(
  object = lm_movies,
  level=0.95
)
```

# Expected values and predictions

```{r}
score_data <- data.frame(
  critics_score = seq(
    from = min(movies$critics_score),
    to = max(movies$critics_score),
    by = 5
  )
)
head(score_data)

predict_none <- predict(
  object = lm_movies,
  newdata = score_data,
  interval = "none",
  level=0.95
)
head(predict_none)

predict_confidence <- predict(
  object = lm_movies,
  newdata = score_data,
  interval = "confidence",
  level=0.95
)
head(predict_confidence)

predict_prediction <- predict(
  object = lm_movies,
  newdata = score_data,
  interval = "prediction",
  level=0.95
)
head(predict_prediction)
```

Now let's add the 
expected values/predictions (red),
expected value confidence intervals (blue),
prediction intervals (purple).

```{r}
plot(
  x = movies$critics_score,
  y = movies$audience_score,
  xlab="Rotten Tomatoes Critics Score", 
  ylab="Rotten Tomatoes Audience Score"
)
abline(
  reg = lm_movies,
  col = "red"
)
lines(
  x = score_data$critics_score,
  y = predict_confidence[,"lwr"],
  col = "blue"
)
lines(
  x = score_data$critics_score,
  y = predict_confidence[,"upr"],
  col = "blue"
)
lines(
  x = score_data$critics_score,
  y = predict_prediction[,"lwr"],
  col = "purple"
)
lines(
  x = score_data$critics_score,
  y = predict_prediction[,"upr"],
  col = "purple"
)
```