---
title: "Transformations of Continuous Random Variables"
author: "Brandon Parmanand"
date: '2022-07-27'
output: html_document
---

## Take your data set from the first assignment of our course. Find a numeric column that interests you.

```{r}
setwd("C:/Users/brand/OneDrive/Documents/GitHub/Prob&Stats")
getwd()
movies.df <- read.csv("movies.csv")
movies.df <- na.omit(movies.df)
library(car)

```


## Plot a histogram of the column of data. Clearly label your plot with "raw data".

```{r}
Runtime = movies.df$runtime
hist(x = Runtime, main = "raw data")
```


## Plot a histogram of your data after center and scaling. Clearly label your plot "center and scale". Comment on how your transformed data is different from your original data.

```{r}
Runtime_Center_Scale = scale(Runtime)
hist(x = Runtime_Center_Scale, main = "center and scale")
# Now the data includes negative numbers but it's based around 0 on histogram
```


## Plot a histogram of your data after transforming the range to $[0,1]$. Clearly label your plot "rescale". Comment on how your transformed data is different from your original data.


```{r}
Runtime_Rescale = scales::rescale(Runtime)
hist(x = Runtime_Rescale, main = "rescale")
# Looks similar but values are closer to 0 than 1
```
## Plot a histogram of your data after applying a log-transform. Clearly label your plot "log-transform". If your data has negative or zero values, rescale your data first. Comment on how your transformed data is different from your original data.


```{r}
Runtime_Log_Transform = log(Runtime)
hist(x = Runtime_Log_Transform, main = "log-transform")
# Histogram looks much more bell shaped than original
```
## Plot a histogram of your data after applying a square-root transform. Clearly label your plot "square-root transform". If your data has negative values, rescale your data first. Comment on how your transformed data is different from your original data.

```{r}
Runtime_Sqrt = sqrt(Runtime)
hist(x = Runtime_Sqrt, main = "square-root transform")
# Histogram looks similar to raw data 
```
## Plot a histogram of your data after applying a power-transform. Clearly label your plot with the family parameter you used. Comment on how your transformed data is different from your original data.

```{r}
v <- as.numeric(Runtime)

car::powerTransform(v, family = "bcPower")

hist((v^-1.39 - 1) / -1.39, main = "bcPower transform")
# Histogram is very bell shaped 
```






